---
title: "Main analysis - SoCult"
author: "Anna Stuckert and Sofie Rødkjær"
date: "24/4/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load packages
```{r cars}
pacman::p_load(
  rethinking,
  brms,
  tidyverse,
  bayesplot,
  viridis,
  dplyr, 
  ggplot2,
  tibble, 
  boot,
  cowplot,
  caret,
  e1071
)

```

## Load data

```{r pressure, echo=FALSE}
#load data

d <- read_csv(~"/Users/Lenovo/Documents/CogSci/4. semester/Social and Cultural Dynamics/Exam/Data/Exam experiment SocCult Anna og Sofie DONE/Social_and_Cultural_Dynamics_in_Cognition_Exam/Analysis and plot scripts/")


##### Initial plots


# Duplicate Bot column 
d$Partner = d$BOT

# Overall cooperation rate for each partner (Bot)
ggplot(d, aes(BOT, PR, fill = Partner)) + geom_bar(stat= "summary") + geom_errorbar(stat="summary", fun.data=mean_se, width=0.3) + theme(legend.position= "none") + ggtitle("Player cooperation for each partner") + ylab("Player cooperation")

# Participant response as a function of time
ggplot(d, aes(x = Trial, y= PR, colour = Partner)) + geom_smooth(alpha = 0.2) + ggtitle("Player cooperation level as a function of time") + xlab("Time aka Trial") + ylab("Player cooperation")
```



## Define models
```{r}
### Baseline model
virk_f0 <- bf(PR ~ 1 + (1 | ID))

### Only BotReputation (Social_Rep)
virk_f1 <- bf(PR ~ 0 + Social_Rep + (0 + Social_Rep | ID))

### Only BotGender 
virk_f2 <- bf(PR ~ 0 + BotGender + (0 + BotGender | ID))

### Interaction between Social_Rep og BotGender 
virk_f3 <- bf(PR ~ 0 + Social_Rep + BotGender + (0 + Social_Rep + BotGender| ID))

virk_f4 <- bf(PR ~ 0 + Social_Rep:BotGender + (0 + Social_Rep:BotGender | ID))

### Interaction between Social_Rep, BotGender og ParticipantGender (Gender)
virk_f5 <- bf(PR ~ 0 + Social_Rep:BotGender + Gender + (0 + Social_Rep:BotGender + Gender | ID))

virk_f6 <- bf(PR ~ 0 + Social_Rep:BotGender:Gender + (0 + Social_Rep:BotGender:Gender | ID))

### Effects of Programmed behavior and learning
virk_f7 <- bf(PR ~ 0 + Social_Rep:BotGender + BRprevious + (0 + Social_Rep:BotGender + BRprevious | ID))
virk_f8 <- bf(PR ~ 0 + Social_Rep:BotGender:BRprevious + (0 + Social_Rep:BotGender:BRprevious | ID))

virk_f9 <- bf(PR ~ 0 + Social_Rep:BotGender + Prog_Beh + (0 + Social_Rep:BotGender + Prog_Beh | ID))
virk_f10 <- bf(PR ~ 0 + Social_Rep:BotGender:Prog_Beh + (0 + Social_Rep:BotGender:Prog_Beh | ID))

virk_f11 <- bf(PR ~ 0 + Social_Rep:BotGender:Prog_Beh + Social_Rep:BotGender:Prog_Beh + mo(Trial) + (0 + Social_Rep:BotGender:Prog_Beh + Social_Rep:BotGender:Prog_Beh + mo(Trial) | ID))

virk_f12 <- bf(PR ~ 0 + Social_Rep:BotGender:Prog_Beh + Social_Rep:BotGender:Prog_Beh:mo(Trial) + (0 + Social_Rep:BotGender:Prog_Beh + Social_Rep:BotGender:Prog_Beh:mo(Trial) | ID))

```

############ MODELS ##############

##### Baseline Model
```{r}
### Baseline model
#Get prior
get_prior(virk_f0, d, family = bernoulli())

"set prior"
prior_f0 <- c(
  prior(normal(0,1.5), class=Intercept),
  prior(normal(0,0.3), class=sd)
) 

## Testing the prior

# Testing the prior in the model
m0_prior <- brm(
  virk_f0,
  d,
  family = bernoulli(),
  prior = prior_f0,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm0_prior'
)

## Standard pp_check
pp_check(m0_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m0_prior)
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

## Fitting the model
m0 <- brm(
  virk_f0,
  d,
  family = bernoulli(),
  prior = prior_f0,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm0'
)

### model quality check
summary(m0)

# - trace plots and trace rank plots
color_scheme_set("viridis")
mcmc_trace(m0, pars="b_Intercept") + theme_classic()
mcmc_rank_overlay(m0, pars="b_Intercept") + theme_classic()

#Quick trace plots for all parameters
plot(m0)

pp_check(m0, nsamples = 100)
## Better pp_check
y_pred <- posterior_linpred(m0)
dens(inv_logit(y_pred))

```

##### Model 1
```{r}
#get prior
get_prior(virk_f1, d, family = bernoulli())

#set prior
prior_f1 <- c(
  prior(normal(0,1.5), class = b),
  prior(normal(0,0.3), class = sd)
) 

## Testing the prior in the model
m1_prior <- brm(
  virk_f1,
  d,
  family = bernoulli(),
  prior = prior_f1,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm1_prior'
)

## Standard pp_check
pp_check(m1_prior, nsamples = 100)
## Better pp_check
y_pred <- posterior_linpred(m1_prior)
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed


# Fitting the model
m1 <- brm(
  virk_f1,
  d,
  family = bernoulli(),
  prior = prior_f1,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm1'
)

### model quality check
summary(m1)

# - trace plots and trace rank plots
color_scheme_set("viridis")
mcmc_trace(m1, pars = "b_Social_RepHigh") + theme_classic()
mcmc_rank_overlay(m1, pars = "b_Social_RepHigh") + theme_classic()

#Quick trace plots for all parameters
plot(m1)

pp_check(m1, nsamples = 100)
## Better pp_check
y_pred <- posterior_linpred(m1)
dens(inv_logit(y_pred))

```

##### Model 2
```{r}
#get prior
get_prior(virk_f2, d, family = bernoulli())

#set prior
prior_f2 <- c(
  prior(normal(0,1.5), class = b),
  prior(normal(0,0.3), class = sd)
) 

## Testing the prior in the model
m2_prior <- brm(
  virk_f2,
  d,
  family = bernoulli(),
  prior = prior_f2,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm2_prior'
)

## Standard pp_check
pp_check(m2_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m2_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

## Fitting the model
m2 <- brm(
  virk_f2,
  d,
  family = bernoulli(),
  prior = prior_f2,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm2'
)

### model quality check
summary(m2)

# - trace plots and trace rank plots
color_scheme_set("viridis")
mcmc_trace(m2, pars = "b_BotGenderF") + theme_classic()
mcmc_rank_overlay(m2, pars = "b_BotGenderF") + theme_classic()

#Quick trace plots for all parameters
plot(m2)

pp_check(m2, nsamples = 100)
## Better pp_check
y_pred <- posterior_linpred(m2)
dens(inv_logit(y_pred))

```

##### Model 3
```{r}
#get prior
get_prior(virk_f3, d, family = bernoulli())

#set prior
prior_f3 <- c(
  prior(normal(0,1.5), class = b), 
  prior(normal(0,.3), class = sd),
  prior(lkj(1), class=cor)
) 

# Testing the prior in the model
m3_prior <- brm(
  virk_f3,
  d,
  family = bernoulli(),
  prior = prior_f3,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm3_prior'
)

## Standard pp_check
pp_check(m3_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m3_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

# Fitting the model
m3 <- brm(
  virk_f3,
  d,
  family = bernoulli(),
  prior = prior_f3,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm3'
)

### model quality check
summary(m3)

# - trace plots and trace rank plots
color_scheme_set("viridis")
mcmc_trace(m3, pars = "b_Social_RepHigh") + theme_classic()
mcmc_rank_overlay(m3, pars = "b_Social_RepHigh") + theme_classic()

#Quick trace plots for all parameters
plot(m3)


## posterior check
pp_check(m3, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m3)
dens(inv_logit(y_pred))

```


##### Model 4
```{r}
#get prior
get_prior(virk_f4, d, family = bernoulli())

#set prior
prior_f4 <- c(
  prior(normal(0,1.5), class = b), 
  prior(normal(0,.3), class = sd),
  prior(lkj(1), class=cor)
) 

## Testing the prior

# Testing the prior in the model
m4_prior <- brm(
  virk_f4,
  d,
  family = bernoulli(),
  prior = prior_f4,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm4_prior'
)

## Standard pp_check
pp_check(m4_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m4_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

# Fitting the model
m4 <- brm(
  virk_f4,
  d,
  family = bernoulli(),
  prior = prior_f4,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm4'
)

### model quality check
summary(m4)

# - trace plots and trace rank plots
color_scheme_set("viridis")
mcmc_trace(m4, pars = "b_Social_RepHigh:BotGenderF") + theme_classic()
mcmc_rank_overlay(m4, pars = "b_Social_RepHigh:BotGenderF") + theme_classic()

#Quick trace plots for all parameters
plot(m4)

pp_check(m4, nsamples = 100)
## Better pp_check
y_pred <- posterior_linpred(m4)
dens(inv_logit(y_pred))


```

##### MODEL COMPARISON 1 #########
```{r}
#adding LOO-criterion to each model
m0 <- add_criterion(m0, c("loo", "waic"))
m1 <- add_criterion(m1, c("loo", "waic"))
m2 <- add_criterion(m2, c("loo", "waic"))
m3 <- add_criterion(m3, c("loo", "waic"))
m4 <- add_criterion(m4, c("loo", "waic"))

#comparison
loo_compare(m0, m1, m2, m3, m4)

#stacking weights
loo_model_weights(m0, m1, m2, m3, m4)

```

##### Converting model estimates into probability space PHASE 1
```{r}

#We take the inverse logit of the log odds provided by the model (estimates) in order to transform the values into probability space.

#extract model summary 
sum4 <- summary(m4)
sum4

#To get population level estimates in inv_logit
df <- sum4[[14]]
df
str(df)
inv_logit(df)

```


##### Model 5
```{r}
#get prior
get_prior(virk_f5, d, family = bernoulli())

"set prior"
prior_f5 <- c(
  prior(normal(0,1.5), class = b), 
  prior(normal(0,.3), class = sd),
  prior(lkj(1), class=cor)
) 

# ## Testing the prior in the model
m5_prior <- brm(
  virk_f5,
  d,
  family = bernoulli(),
  prior = prior_f5,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm5_prior.csv'
)

# ## Standard pp_check
pp_check(m5_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m5_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

## Fitting the model
m5 <- brm(
  virk_f5,
  d,
  family = bernoulli(),
  prior = prior_f5,
  sample_prior = T,
  chains = 4, cores =4,
  file = 'm5'
)

### model quality check
summary(m5)

# - trace plots and trace rank plots
color_scheme_set("viridis")
mcmc_trace(m5, pars = "b_Social_RepHigh:BotGenderF") + theme_classic()
mcmc_rank_overlay(m5, pars = "b_Social_RepHigh:BotGenderF") + theme_classic()

#Quick trace plots for all parameters
plot(m5)

pp_check(m5, nsamples = 100)
## Better pp_check
y_pred <- posterior_linpred(m5)
dens(inv_logit(y_pred))

#Quick trace plots for all parameters
plot(m5)

```


##### Model 6
```{r}
#get prior
get_prior(virk_f6, d, family = bernoulli())

#set prior
prior_f6 <- c(
  prior(normal(0,1.5), class = b),
  prior(normal(0,.3), class = sd),
  prior(lkj(1), class=cor)
) 
## Testing the prior

## Testing the prior in the model
m6_prior <- brm(
  virk_f6,
  d,
  family = bernoulli(),
  prior = prior_f6,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm6_prior'
)

## Standard pp_check
pp_check(m6_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m6_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

# Fitting the model
m6 <- brm(
  virk_f6,
  d,
  family = bernoulli(),
  prior = prior_f6,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm6'
)
### model quality check
summary(m6)

# - trace plots and trace rank plots
color_scheme_set("viridis")
mcmc_trace(m6, pars = "b_Social_RepHigh:BotGenderF:GenderKvinde") + theme_classic()
mcmc_rank_overlay(m6, pars = "b_Social_RepHigh:BotGenderF:GenderKvinde") + theme_classic()

#Quick trace plots for all parameters
plot(m6)

## posterior check
pp_check(m6, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m6)
dens(inv_logit(y_pred))

```


##### MODEL COMPARISON 2 #########
```{r}
#adding LOO criterions to each new model
m5 <- add_criterion(m5, c("loo", "waic"))
m6 <- add_criterion(m6, c("loo", "waic"))

#comparison
loo_compare(m4, m5, m6)
#Stacking weights
loo_model_weights(m4, m5, m6)

```

#### Converting model estimates into probability space PHASE 2
```{r}
#We take the inverse logit of the log odds provided by the model (estimates) in order to transform the values into probability space.

#extract model summary
sum5 <- summary(m5)
sum5

#To get population level estimates in inv_logit
df <- sum5[[14]]
df
str(df)
inv_logit(df)

```


##### Models with a direct reciprocity
```{r}

#set prior for all models testing direct reciprocity
prior_dr <- c(
  prior(normal(0,1.5), class = b),
  prior(normal(0,.3), class = sd),
  prior(lkj(1), class=cor)
) 

#Running each model

### Model 7
# Prior
m7_prior <- brm(
  virk_f7,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm7_prior' 
)

# Standard pp_check
pp_check(m7_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m7_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

# Fitting the model
m7 <- brm(
  virk_f7,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm7' 
)

### model quality check
summary(m7)

# - trace plots and trace rank plots
color_scheme_set("viridis")
mcmc_trace(m7, pars = "b_Social_RepHigh:BotGenderF") + theme_classic()
mcmc_rank_overlay(m7, pars = "b_Social_RepHigh:BotGenderF") + theme_classic()

#Quick trace plots for all parameters
plot(m7)

pp_check(m7, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m7) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed



### Model 8
# Prior
m8_prior <- brm(
  virk_f8,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm8_prior' 
)

# Standard pp_check
pp_check(m8_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m8_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

# Fitting the model
m8 <- brm(
  virk_f8,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm8' 
)

### model quality check
summary(m8)

color_scheme_set("viridis")
mcmc_trace(m8, pars = "b_Social_RepHigh:BotGenderF:BRpreviousCooperate") + theme_classic()
mcmc_rank_overlay(m8, pars = "b_Social_RepHigh:BotGenderF:BRpreviousCooperate") + theme_classic()

#Quick trace plots for all parameters
plot(m8)

pp_check(m8, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m8) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed


### Model 9
# Prior
m9_prior <- brm(
  virk_f9,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm9_prior' 
)

# Standard pp_check
pp_check(m9_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m9_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

# Fitting the model
m9 <- brm(
  virk_f9,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm9' 
)

### model quality check
summary(m9)

color_scheme_set("viridis")
mcmc_trace(m9, pars = "b_Social_RepHigh:BotGenderF") + theme_classic()
mcmc_rank_overlay(m9, pars = "b_Social_RepHigh:BotGenderF") + theme_classic()

#Quick trace plots for all parameters
plot(m9)

pp_check(m9, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m9) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed


### Model 7
# Prior
m10_prior <- brm(
  virk_f10,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm10_prior' 
)

# Standard pp_check
pp_check(m10_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m10_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

# Fitting the model
m10 <- brm(
  virk_f10,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm10' 
)

### model quality check
summary(m10)

color_scheme_set("viridis")
mcmc_trace(m10, pars = "b_Social_RepHigh:BotGenderF:Prog_BehBad") + theme_classic()
mcmc_rank_overlay(m10, pars = "b_Social_RepHigh:BotGenderF:Prog_BehBad") + theme_classic()

#Quick trace plots for all parameters
plot(m10)

pp_check(m10, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m10) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed


### Model 11
# Prior
m11_prior <- brm(
  virk_f11,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm11_prior' 
)

# Standard pp_check
pp_check(m11_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m11_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

# Fitting the model
m11 <- brm(
  virk_f11,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm11' 
)

### model quality check
summary(m11)

color_scheme_set("viridis")
mcmc_trace(m11, pars = "b_Social_RepHigh:BotGenderF:Prog_BehBad") + theme_classic()
mcmc_rank_overlay(m11, pars = "b_Social_RepHigh:BotGenderF:Prog_BehBad") + theme_classic()

#Quick trace plots for all parameters
plot(m11)

pp_check(m11, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m11) 
dens(inv_logit(y_pred)) #

### Model 12 - The best model, so also with prior checks 
# Prior
m12_prior <- brm(
  virk_f12,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = "only",
  chains = 4, cores = 4,
  file = 'm12_prior' 
)

# Standard pp_check
pp_check(m12_prior, nsamples = 100)

## Better pp_check
y_pred <- posterior_linpred(m12_prior) 
dens(inv_logit(y_pred)) #densityplot that has been inverse logit-transformed

# Fitting the model
m12 <- brm(
  virk_f12,
  d,
  family = bernoulli(),
  prior = prior_dr,
  sample_prior = T,
  chains = 4, cores = 4,
  file = 'm12' 
)



### model quality check
# options(max.print = 10000)
print(summary(m12), digits = 5)

# - trace plots and trace rank plots
color_scheme_set("viridis")
mcmc_trace(m12, pars = "b_Social_RepHigh:BotGenderF:Prog_BehBad") + theme_classic()
mcmc_rank_overlay(m12, pars = "b_Social_RepHigh:BotGenderF:Prog_BehBad") + theme_classic()

#Quick trace plots for all parameters
plot(m12)

## posterior check
pp_check(m12, nsamples = 100)


## Better pp_check
y_pred <- posterior_linpred(m12)
dens(inv_logit(y_pred))
```


##### MODEL COMPARISON 3 #########
```{r}

#Adding LOO-criterion to each new model
m7 <- add_criterion(m7, c("loo", "waic"))
m8 <- add_criterion(m8, c("loo", "waic"))
m9 <- add_criterion(m9, c("loo", "waic"))
m10 <- add_criterion(m10, c("loo", "waic"))
m11 <- add_criterion(m11, c("loo", "waic"))
m12 <- add_criterion(m12, c("loo", "waic"))

#Comparison
loo_compare(m4, m7, m8, m9, m10, m11, m12)
#stacking weights
loo_model_weights(m4, m7, m8, m9, m10, m11, m12)

```

##### Converting model estimates into probability space PHASE 3
```{r}

#We take the inverse logit of the log odds provided by the model (estimates) in order to transform the values into probability space.

#extract model summary
sum12 <- summary(m12)
sum12

#to get population level estimates in inv_logit
df <- sum12[[14]]
df
str(df)
inv_logit(df)

```
 
##### Hypotheses

Manual hypothesis testing in probability space

- Because we want to work in probability space we made a manual hypothesis testing procedure:
 . extract the posteriors from the model: post <- posterior_samples(model)
 . check the names of columns in post to see what things are called (in particular the ones starting w b)
 . perform the inv_logit on the b columns (to go to % space)
 . perform hypotheses test

Phase 1

```{r}
#extract the posteriors from the model: post <- posterior_samples(model)
post_p1 <- posterior_samples(m4)

#How much have the posterior betas and SD learned from data, compared to priors - density plots of prior vs posterior distributions

#b_Social_RepHigh_BotGenderF
ggplot(post_p1) + geom_density(aes(post_p1$'prior_b', fill = "prior")) + geom_density(aes(post_p1$'b_Social_RepHigh:BotGenderF', fill = "posterior")) + xlab("Parameter values")

#b_Social_RepHigh_BotGenderM 
ggplot(post_p1) + geom_density(aes(post_p1$'prior_b', fill = "prior")) + geom_density(aes(post_p1$'b_Social_RepHigh:BotGenderM', fill = "posterior"))+ xlab("Parameter values")

#b_Social_RepLow_BotGenderF
ggplot(post_p1) + geom_density(aes(post_p1$'prior_b', fill = "prior")) + geom_density(aes(post_p1$'b_Social_RepLow:BotGenderF', fill = "posterior"))+ xlab("Parameter values")

#b_Social_RepLow_BotGenderM
ggplot(post_p1) + geom_density(aes(post_p1$'prior_b', fill = "prior")) + geom_density(aes(post_p1$'b_Social_RepLow:BotGenderM', fill = "posterior")) + xlab("Parameter values")

#sd_ID__Social_RepHigh:BotGenderF
ggplot(post_p1) + geom_density(aes(post_p1$'sd_ID__Social_RepHigh:BotGenderF', fill = "posterior")) + geom_density(aes(post_p1$'prior_sd_ID', fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepHigh:BotGenderM
ggplot(post_p1) + geom_density(aes(post_p1$'sd_ID__Social_RepHigh:BotGenderM', fill = "posterior")) + geom_density(aes(post_p1$'prior_sd_ID', fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepLow:BotGenderF
ggplot(post_p1) + geom_density(aes(post_p1$'sd_ID__Social_RepLow:BotGenderF', fill = "posterior")) + geom_density(aes(post_p1$'prior_sd_ID', fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepLow:BotGenderF
ggplot(post_p1) + geom_density(aes(post_p1$'sd_ID__Social_RepLow:BotGenderM', fill = "posterior")) + geom_density(aes(post_p1$'prior_sd_ID', fill = "prior"))+ xlab("Parameter values")

#rename colums
colnames(post_p1)[colnames(post_p1) == "b_Social_RepHigh:BotGenderF"] <- "b_Social_RepHigh_BotGenderF"
colnames(post_p1)[colnames(post_p1) == "b_Social_RepHigh:BotGenderM"] <- "b_Social_RepHigh_BotGenderM"
colnames(post_p1)[colnames(post_p1) == "b_Social_RepLow:BotGenderF"] <- "b_Social_RepLow_BotGenderF"
colnames(post_p1)[colnames(post_p1) == "b_Social_RepLow:BotGenderM"] <- "b_Social_RepLow_BotGenderM"

post_p1$b_Social_RepHigh_BotGenderF <- inv_logit(post_p1$b_Social_RepHigh_BotGenderF)
post_p1$b_Social_RepHigh_BotGenderM <- inv_logit(post_p1$b_Social_RepHigh_BotGenderM)
post_p1$b_Social_RepLow_BotGenderF <- inv_logit(post_p1$b_Social_RepLow_BotGenderF)
post_p1$b_Social_RepLow_BotGenderM <- inv_logit(post_p1$b_Social_RepLow_BotGenderM)

post_p1 <- as.data.frame(post_p1)

#Hypothesis testing

## H1: People with high reputation are cooperated with more than people with low reputation
hypothesis(post_p1, "(b_Social_RepHigh_BotGenderM + b_Social_RepHigh_BotGenderF)/2 > 
           (b_Social_RepLow_BotGenderM + b_Social_RepLow_BotGenderF)/2")

plot(hypothesis(post_p1, "(b_Social_RepHigh_BotGenderM + b_Social_RepHigh_BotGenderF)/2 > 
           (b_Social_RepLow_BotGenderM + b_Social_RepLow_BotGenderF)/2"))

## H2: Female bots will be cooperated with more than male bots
hypothesis(post_p1, "(b_Social_RepHigh_BotGenderF + b_Social_RepLow_BotGenderF)/2 > 
           (b_Social_RepHigh_BotGenderM + b_Social_RepLow_BotGenderM)/2")

plot(hypothesis(post_p1, "(b_Social_RepHigh_BotGenderF + b_Social_RepLow_BotGenderF)/2 > 
           (b_Social_RepHigh_BotGenderM + b_Social_RepLow_BotGenderM)/2"))


## H3: Females with low reputation will be cooperated with more than male bots with low reputation
hypothesis(post_p1, "b_Social_RepLow_BotGenderF > b_Social_RepLow_BotGenderM")

hypothesis(post_p1, "b_Social_RepHigh_BotGenderM > b_Social_RepHigh_BotGenderF")


plot(hypothesis(post_p1, "b_Social_RepLow_BotGenderF > b_Social_RepLow_BotGenderM"))

plot(hypothesis(post_p1, "b_Social_RepHigh_BotGenderM > b_Social_RepHigh_BotGenderF"))

```


Phase 2
```{r}
#extract the posteriors from the model: post <- posterior_samples(model)
post_p2 <- posterior_samples(m5)

colnames(post_p2)[colnames(post_p2) == "b_Social_RepHigh:BotGenderF"] <- "b_Social_RepHigh_BotGenderF"
colnames(post_p2)[colnames(post_p2) == "b_Social_RepHigh:BotGenderM"] <- "b_Social_RepHigh_BotGenderM"
colnames(post_p2)[colnames(post_p2) == "b_Social_RepLow:BotGenderF"] <- "b_Social_RepLow_BotGenderF"
colnames(post_p2)[colnames(post_p2) == "b_Social_RepLow:BotGenderM"] <- "b_Social_RepLow_BotGenderM"

post_p2$b_GenderKvinde <- inv_logit(post_p2$b_GenderKvinde)
post_p2$b_GenderMand<- inv_logit(post_p2$b_GenderMand)
post_p2$b_Social_RepHigh_BotGenderF <- inv_logit(post_p2$b_Social_RepHigh_BotGenderF)
post_p2$b_Social_RepHigh_BotGenderM <- inv_logit(post_p2$b_Social_RepHigh_BotGenderM)
post_p2$b_Social_RepLow_BotGenderF <- inv_logit(post_p2$b_Social_RepLow_BotGenderF)
post_p2$b_Social_RepLow_BotGenderM <- inv_logit(post_p2$b_Social_RepLow_BotGenderM)

#How much have the posterior betas and SD learned from data, compared to priors - density plots of prior vs posterior distributions

#b_GenderKvinde
ggplot(post_p2) + geom_density(aes(post_p2$prior_b, fill = "prior")) + geom_density(aes(post_p2$b_GenderKvinde, fill = "posterior")) + xlab("Parameter values")

#b_GenderKvinde
ggplot(post_p2) + geom_density(aes(post_p2$prior_b, fill = "prior")) + geom_density(aes(post_p2$b_GenderMand, fill = "posterior")) + xlab("Parameter values")

#b_Social_RepHigh_BotGenderF
ggplot(post_p2) +  geom_density(aes(post_p2$prior_b, fill = "prior")) + geom_density(aes(post_p2$b_Social_RepHigh_BotGenderF, fill = "posterior")) + xlab("Parameter values")

#b_Social_RepHigh_BotGenderM
ggplot(post_p2) +  geom_density(aes(post_p2$prior_b, fill = "prior")) + geom_density(aes(post_p2$b_Social_RepHigh_BotGenderM, fill = "posterior"))+ xlab("Parameter values")

#b_Social_RepLow_BotGenderF
ggplot(post_p2) +  geom_density(aes(post_p2$prior_b, fill = "prior")) + geom_density(aes(post_p2$b_Social_RepLow_BotGenderF, fill = "posterior")) + xlab("Parameter values")

#b_Social_RepLow_BotGenderM
ggplot(post_p2) +  geom_density(aes(post_p2$prior_b, fill = "prior")) + geom_density(aes(post_p2$b_Social_RepLow_BotGenderM, fill = "posterior")) + xlab("Parameter values")

#SD_GenderKvinde
ggplot(post_p2) + geom_density(aes(post_p2$prior_sd_ID, fill = "prior")) + geom_density(aes(post_p2$sd_ID__GenderKvinde, fill = "posterior")) + xlab("Parameter values")

#sd_GenderMand
ggplot(post_p2) + geom_density(aes(post_p2$prior_sd_ID, fill = "prior")) + geom_density(aes(post_p2$sd_ID__GenderMand, fill = "posterior")) + xlab("Parameter values")

#sd_ID__Social_RepHigh:BotGenderF
ggplot(post_p2) + geom_density(aes(post_p2$`sd_ID__Social_RepHigh:BotGenderF`, fill = "posterior")) + geom_density(aes(post_p2$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepHigh:BotGenderM
ggplot(post_p2) + geom_density(aes(post_p2$`sd_ID__Social_RepHigh:BotGenderM`, fill = "posterior")) + geom_density(aes(post_p2$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepLow:BotGenderF
ggplot(post_p2) + geom_density(aes(post_p2$`sd_ID__Social_RepLow:BotGenderF`, fill = "posterior")) + geom_density(aes(post_p2$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepLow:BotGenderF
ggplot(post_p2) + geom_density(aes(post_p2$`sd_ID__Social_RepLow:BotGenderM`, fill = "posteriors")) + geom_density(aes(post_p2$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")

#hypothesis testing

## H4: We expect a tendency to cooperate more with a bot of one's own gender
hypothesis(post_p2, "((b_Social_RepHigh_BotGenderM + b_GenderMand) + (b_Social_RepHigh_BotGenderF + b_GenderKvinde))/2 >
           ((b_Social_RepHigh_BotGenderM + b_GenderKvinde) + (b_Social_RepHigh_BotGenderF + b_GenderMand))/2")

plot(hypothesis(post_p2, "((b_Social_RepHigh_BotGenderM + b_GenderMand) + 
           (b_Social_RepHigh_BotGenderF + b_GenderKvinde))/2 >
           ((b_Social_RepHigh_BotGenderM + b_GenderKvinde) + 
           (b_Social_RepHigh_BotGenderF + b_GenderMand))/2"))

```

Phase 3
```{r}
#extract the posteriors from the model: post <- posterior_samples(model)
post_p3 <- posterior_samples(m12)

# Rename columns, so they don't have ":"
colnames(post_p3)[colnames(post_p3) == "b_Social_RepHigh:BotGenderF:Prog_BehGood"] <- "b_Social_RepHigh_BotGenderF_Prog_BehGood"
colnames(post_p3)[colnames(post_p3) == "b_Social_RepHigh:BotGenderF:Prog_BehBad"] <- "b_Social_RepHigh_BotGenderF_Prog_BehBad"
colnames(post_p3)[colnames(post_p3) == "b_Social_RepHigh:BotGenderM:Prog_BehGood"] <- "b_Social_RepHigh_BotGenderM_Prog_BehGood"
colnames(post_p3)[colnames(post_p3) == "b_Social_RepHigh:BotGenderM:Prog_BehBad"] <- "b_Social_RepHigh_BotGenderM_Prog_BehBad"
colnames(post_p3)[colnames(post_p3) == "b_Social_RepLow:BotGenderF:Prog_BehGood"] <- "b_Social_RepLow_BotGenderF_Prog_BehGood"
colnames(post_p3)[colnames(post_p3) == "b_Social_RepLow:BotGenderF:Prog_BehBad"] <- "b_Social_RepLow_BotGenderF_Prog_BehBad"
colnames(post_p3)[colnames(post_p3) == "b_Social_RepLow:BotGenderM:Prog_BehGood"] <- "b_Social_RepLow_BotGenderM_Prog_BehGood"
colnames(post_p3)[colnames(post_p3) == "b_Social_RepLow:BotGenderM:Prog_BehBad"] <- "b_Social_RepLow_BotGenderM_Prog_BehBad"

colnames(post_p3)[colnames(post_p3) == "bsp_Social_RepHigh:BotGenderF:Prog_BehGood:moTrial"] <- "bsp_Social_RepHigh_BotGenderF_Prog_BehGood_moTrial"
colnames(post_p3)[colnames(post_p3) == "bsp_Social_RepHigh:BotGenderF:Prog_BehBad:moTrial"] <- "bsp_Social_RepHigh_BotGenderF_Prog_BehBad_moTrial"
colnames(post_p3)[colnames(post_p3) == "bsp_Social_RepHigh:BotGenderM:Prog_BehGood:moTrial"] <- "bsp_Social_RepHigh_BotGenderM_Prog_BehGood_moTrial"
colnames(post_p3)[colnames(post_p3) == "bsp_Social_RepHigh:BotGenderM:Prog_BehBad:moTrial"] <- "bsp_Social_RepHigh_BotGenderM_Prog_BehBad_moTrial"
colnames(post_p3)[colnames(post_p3) == "bsp_Social_RepLow:BotGenderF:Prog_BehGood:moTrial"] <- "bsp_Social_RepLow_BotGenderF_Prog_BehGood_moTrial"
colnames(post_p3)[colnames(post_p3) == "bsp_Social_RepLow:BotGenderF:Prog_BehBad:moTrial"] <- "bsp_Social_RepLow_BotGenderF_Prog_BehBad_moTrial"
colnames(post_p3)[colnames(post_p3) == "bsp_Social_RepLow:BotGenderM:Prog_BehGood:moTrial"] <- "bsp_Social_RepLow_BotGenderM_Prog_BehGood_moTrial"
colnames(post_p3)[colnames(post_p3) == "bsp_Social_RepLow:BotGenderM:Prog_BehBad:moTrial"] <- "bsp_Social_RepLow_BotGenderM_Prog_BehBad_moTrial"

#adding mo_trial estimates to calculate parameter estimates for main effects

post_p3$b_Social_RepHigh_BotGenderF_Prog_BehGood <- post_p3$b_Social_RepHigh_BotGenderF_Prog_BehGood+(post_p3$bsp_Social_RepHigh_BotGenderF_Prog_BehGood_moTrial*80)

post_p3$b_Social_RepHigh_BotGenderM_Prog_BehGood <- post_p3$b_Social_RepHigh_BotGenderM_Prog_BehGood+(post_p3$bsp_Social_RepHigh_BotGenderM_Prog_BehGood_moTrial*80)

post_p3$b_Social_RepLow_BotGenderF_Prog_BehGood <- post_p3$b_Social_RepLow_BotGenderF_Prog_BehGood+(post_p3$bsp_Social_RepLow_BotGenderF_Prog_BehGood_moTrial*80)

post_p3$b_Social_RepLow_BotGenderM_Prog_BehGood <- post_p3$b_Social_RepLow_BotGenderM_Prog_BehGood+(post_p3$bsp_Social_RepLow_BotGenderM_Prog_BehGood_moTrial*80)

post_p3$b_Social_RepHigh_BotGenderF_Prog_BehBad <- post_p3$b_Social_RepHigh_BotGenderF_Prog_BehBad+(post_p3$bsp_Social_RepHigh_BotGenderF_Prog_BehBad_moTrial*80)

post_p3$b_Social_RepHigh_BotGenderM_Prog_BehBad <- post_p3$b_Social_RepHigh_BotGenderM_Prog_BehBad+(post_p3$bsp_Social_RepHigh_BotGenderM_Prog_BehBad_moTrial*80)


post_p3$b_Social_RepLow_BotGenderF_Prog_BehBad <- post_p3$b_Social_RepLow_BotGenderF_Prog_BehBad+(post_p3$bsp_Social_RepLow_BotGenderF_Prog_BehBad_moTrial*80)

post_p3$b_Social_RepLow_BotGenderM_Prog_BehBad <- post_p3$b_Social_RepLow_BotGenderM_Prog_BehBad+(post_p3$bsp_Social_RepLow_BotGenderM_Prog_BehBad_moTrial*80)

#How much have the posterior betas and SD learned from data, compared to priors - density plots of prior vs posterior distributions
# GOOD BEHAVIOR

#b_Social_RepHigh_BotGenderF:Prog_BehGood
ggplot(post_p3) + geom_density(aes(post_p3$prior_b, fill = "prior")) + geom_density(aes(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehGood, fill = "posterior")) + xlab("Parameter values")

#b_Social_RepHigh_BotGenderM_Prog_BehGood
ggplot(post_p3) + geom_density(aes(post_p3$prior_b, fill = "prior")) + geom_density(aes(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehGood, fill = "posterior"))+ xlab("Parameter values")

#b_Social_RepLow_BotGenderF_Prog_BehGood
ggplot(post_p3) + geom_density(aes(post_p3$prior_b, fill = "prior")) + geom_density(aes(post_p3$b_Social_RepLow_BotGenderF_Prog_BehGood, fill = "posterior"))+ xlab("Parameter values")

#b_Social_RepLow_BotGenderM_Prog_BehGood
ggplot(post_p3) + geom_density(aes(post_p3$prior_b, fill = "prior")) + geom_density(aes(post_p3$b_Social_RepLow_BotGenderM_Prog_BehGood, fill = "posterior")) + xlab("Parameter values")

#sd_ID__Social_RepHigh_BotGenderF
ggplot(post_p3) + geom_density(aes(post_p3$'sd_ID__Social_RepHigh:BotGenderF:Prog_BehGood', fill = "posterior")) + geom_density(aes(post_p3$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepHigh:BotGenderM
ggplot(post_p3) + geom_density(aes(post_p3$'sd_ID__Social_RepHigh:BotGenderM:Prog_BehGood', fill = "posterior")) + geom_density(aes(post_p3$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepLow:BotGenderF
ggplot(post_p3) + geom_density(aes(post_p3$'sd_ID__Social_RepLow:BotGenderF:Prog_BehGood', fill = "posterior")) + geom_density(aes(post_p3$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepLow:BotGenderF
ggplot(post_p3) + geom_density(aes(post_p3$'sd_ID__Social_RepLow:BotGenderM:Prog_BehGood', fill = "posterior")) + geom_density(aes(post_p3$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")


# BAD BEHAVIOR

#b_Social_RepHigh_BotGenderF:Prog_BehBad
ggplot(post_p3) + geom_density(aes(post_p3$prior_b, fill = "prior")) + geom_density(aes(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehBad, fill = "posterior")) + xlab("Parameter values")

#b_Social_RepHigh_BotGenderM_Prog_BehBad
ggplot(post_p3) + geom_density(aes(post_p3$prior_b, fill = "prior")) + geom_density(aes(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehBad, fill = "posterior"))+ xlab("Parameter values")

#b_Social_RepLow_BotGenderF_Prog_BehBad
ggplot(post_p3) + geom_density(aes(post_p3$prior_b, fill = "prior")) + geom_density(aes(post_p3$b_Social_RepLow_BotGenderF_Prog_BehBad, fill = "posterior"))+ xlab("Parameter values")

#b_Social_RepLow_BotGenderM_Prog_BehBad
ggplot(post_p3) + geom_density(aes(post_p3$prior_b, fill = "prior")) + geom_density(aes(post_p3$b_Social_RepLow_BotGenderM_Prog_BehBad, fill = "posterior")) + xlab("Parameter values")

#sd_ID__Social_RepHigh:BotGenderF
ggplot(post_p3) + geom_density(aes(post_p3$'sd_ID__Social_RepHigh:BotGenderF:Prog_BehBad', fill = "posterior")) + geom_density(aes(post_p3$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepHigh:BotGenderM
ggplot(post_p3) + geom_density(aes(post_p3$'sd_ID__Social_RepHigh:BotGenderM:Prog_BehBad', fill = "posterior")) + geom_density(aes(post_p3$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepLow:BotGenderF
ggplot(post_p3) + geom_density(aes(post_p3$'sd_ID__Social_RepLow:BotGenderF:Prog_BehBad', fill = "posterior")) + geom_density(aes(post_p3$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")

#sd_ID__Social_RepLow:BotGenderF
ggplot(post_p3) + geom_density(aes(post_p3$'sd_ID__Social_RepLow:BotGenderM:Prog_BehBad', fill = "posterior")) + geom_density(aes(post_p3$prior_sd_ID, fill = "prior"))+ xlab("Parameter values")



### Find estimates, error and CI
#estimate for each parameter
mean(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehGood)
mean(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehGood )
mean(post_p3$b_Social_RepLow_BotGenderF_Prog_BehGood)
mean(post_p3$b_Social_RepLow_BotGenderM_Prog_BehGood)
mean(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehBad)
mean(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehBad)
mean(post_p3$b_Social_RepLow_BotGenderF_Prog_BehBad)
mean(post_p3$b_Social_RepLow_BotGenderM_Prog_BehBad)

#estimated error for each parameter
sd(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehGood)
sd(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehGood)
sd(post_p3$b_Social_RepLow_BotGenderF_Prog_BehGood)
sd(post_p3$b_Social_RepLow_BotGenderM_Prog_BehGood)
sd(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehBad)
sd(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehBad)
sd(post_p3$b_Social_RepLow_BotGenderF_Prog_BehBad)
sd(post_p3$b_Social_RepLow_BotGenderM_Prog_BehBad)

#CI's for each parameter
quantile(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehGood, c(.05, .95))
quantile(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehGood , c(.05, .95))
quantile(post_p3$b_Social_RepLow_BotGenderF_Prog_BehGood, c(.05, .95))
quantile(post_p3$b_Social_RepLow_BotGenderM_Prog_BehGood, c(.05, .95))
quantile(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehBad, c(.05, .95))
quantile(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehBad, c(.05, .95))
quantile(post_p3$b_Social_RepLow_BotGenderF_Prog_BehBad, c(.05, .95))
quantile(post_p3$b_Social_RepLow_BotGenderM_Prog_BehBad, c(.05, .95))

#probability estimate for each parameter
inv_logit(mean(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehGood))
inv_logit(mean(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehGood))
inv_logit(mean(post_p3$b_Social_RepLow_BotGenderF_Prog_BehGood))
inv_logit(mean(post_p3$b_Social_RepLow_BotGenderM_Prog_BehGood))
inv_logit(mean(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehBad))
inv_logit(mean(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehBad))
inv_logit(mean(post_p3$b_Social_RepLow_BotGenderF_Prog_BehBad))
inv_logit(mean(post_p3$b_Social_RepLow_BotGenderM_Prog_BehBad))

#perform the inv_logit on the b columns (to go to % space)
post_p3$b_Social_RepHigh_BotGenderF_Prog_BehGood <- inv_logit(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehGood)
post_p3$b_Social_RepHigh_BotGenderM_Prog_BehGood <- inv_logit(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehGood)
post_p3$b_Social_RepLow_BotGenderF_Prog_BehGood <- inv_logit(post_p3$b_Social_RepLow_BotGenderF_Prog_BehGood)
post_p3$b_Social_RepLow_BotGenderM_Prog_BehGood <- inv_logit(post_p3$b_Social_RepLow_BotGenderM_Prog_BehGood)

post_p3$b_Social_RepHigh_BotGenderF_Prog_BehBad <- inv_logit(post_p3$b_Social_RepHigh_BotGenderF_Prog_BehBad)
post_p3$b_Social_RepHigh_BotGenderM_Prog_BehBad <- inv_logit(post_p3$b_Social_RepHigh_BotGenderM_Prog_BehBad)
post_p3$b_Social_RepLow_BotGenderF_Prog_BehBad <- inv_logit(post_p3$b_Social_RepLow_BotGenderF_Prog_BehBad)
post_p3$b_Social_RepLow_BotGenderM_Prog_BehBad <- inv_logit(post_p3$b_Social_RepLow_BotGenderM_Prog_BehBad)

summary(post_p3)

#hypothesis testing

## H5a: General effect of direct reciprocity?
hypothesis(post_p3, "b_Social_RepHigh_BotGenderF_Prog_BehGood +
           b_Social_RepHigh_BotGenderM_Prog_BehGood +
           b_Social_RepLow_BotGenderF_Prog_BehGood +
           b_Social_RepLow_BotGenderM_Prog_BehGood >
           
           b_Social_RepHigh_BotGenderF_Prog_BehBad +
           b_Social_RepHigh_BotGenderM_Prog_BehBad +
           b_Social_RepLow_BotGenderF_Prog_BehBad +
           b_Social_RepLow_BotGenderM_Prog_BehBad")

plot(hypothesis(post_p3, "b_Social_RepHigh_BotGenderF_Prog_BehGood +
           b_Social_RepHigh_BotGenderM_Prog_BehGood +
           b_Social_RepLow_BotGenderF_Prog_BehGood +
           b_Social_RepLow_BotGenderM_Prog_BehGood >
           
           b_Social_RepHigh_BotGenderF_Prog_BehBad +
           b_Social_RepHigh_BotGenderM_Prog_BehBad +
           b_Social_RepLow_BotGenderF_Prog_BehBad +
           b_Social_RepLow_BotGenderM_Prog_BehBad"))


#h5b - different effects of prog_beh for social_rep
hypothesis(post_p3, "((b_Social_RepHigh_BotGenderF_Prog_BehGood +
           b_Social_RepHigh_BotGenderM_Prog_BehGood)/2 -
           (b_Social_RepHigh_BotGenderF_Prog_BehBad +
           b_Social_RepHigh_BotGenderM_Prog_BehBad)/2) >
           
           ((b_Social_RepLow_BotGenderF_Prog_BehGood +
           b_Social_RepLow_BotGenderM_Prog_BehGood)/2 -
           (b_Social_RepLow_BotGenderF_Prog_BehBad +
           b_Social_RepLow_BotGenderM_Prog_BehBad)/2)")

plot(hypothesis(post_p3, "((b_Social_RepHigh_BotGenderF_Prog_BehGood +
           b_Social_RepHigh_BotGenderM_Prog_BehGood)/2 -
           (b_Social_RepHigh_BotGenderF_Prog_BehBad +
           b_Social_RepHigh_BotGenderM_Prog_BehBad)/2) >
           
           ((b_Social_RepLow_BotGenderF_Prog_BehGood +
           b_Social_RepLow_BotGenderM_Prog_BehGood)/2 -
           (b_Social_RepLow_BotGenderF_Prog_BehBad +
           b_Social_RepLow_BotGenderM_Prog_BehBad)/2)"))

```


MODEL PREDICTIONS  - REAL VS MODEL PREDICTED DATA

M3

```{r}
# To get model predictions
predictions=predict(m3, type = "response")
d$prediction = predictions[,1]

d$PR <- as.numeric(d$PR)

# To make a plot comparing model predictions with actual data. Actual data = red, predictions = blue
dens(d$PR, col = "red") 
class(d$prediction)
dens(d$prediction, col = "blue")

# To create a confusion matrix to get accuracy
d$Predictionsm3[d$prediction>0.5]=1 
d$Predictionsm3[d$prediction<=0.5]=0

class(d$Predictionsm3)
class(d$PR)
d$Predictionsm3 <- as.factor(d$Predictionsm3)
d$PR <- as.factor(d$PR)
CM3 <- confusionMatrix(data = d$Predictionsm3, reference = d$PR)
CM3 #to see accuracy of the model

```

M4.5
```{r}
# To get model predictions
predictions=predict(m4.5, type = "response")
d$predictionm45 = predictions[,1]

# To make a plot comparing model predictions with actual data. Actual data = red, predictions = blue
dens(d$PR, col = "red") 
class(d$predict)
dens(d$predictionm45, col = "blue")

# To create a confusion matrix to get accuracy
d$Predictionsm4.5[d$prediction>0.5]=1 
d$Predictionsm4.5[d$prediction<=0.5]=0

class(d$Predictionsm4.5)
class(d$PR)
d$Predictionsm4.5 <- as.factor(d$Predictionsm4.5)
d$PR <- as.factor(d$PR)
CM4.5<- confusionMatrix(data = d$Predictionsm4.5, reference = d$PR)
CM4.5 #to see accuracy of the model

```

M12
```{r}
# To get model predictions
predictions=predict(m12, type = "response")
d$predictionm12 = predictions[,1]

# To make a plot comparing model predictions with actual data. Actual data = red, predictions = blue
dens(d$PR, col = "red") 
class(d$predict)
dens(d$predictionm12, col = "blue")

# To create a confusion matrix to get accuracy
d$Predictionsm12[d$predictionm12>0.5]=1 
d$Predictionsm12[d$predictionm12<=0.5]=0

class(d$Predictionsm12)
class(d$PR)
d$Predictionsm12 <- as.factor(d$Predictionsm12)
d$PR <- as.factor(d$PR)
CM12 <- confusionMatrix(data = d$Predictionsm12, reference = d$PR)
CM12 #to see accuracy of the model

```


For data plots, see plot code
